A* with Perfect Potentials

### 2020-05-15 paper/ch_potentials.tex
switch to acm class

\documentclass[a4paper,UKenglish,cleveref, autoref]{lipics-v2019}
%This is a template for producing LIPIcs articles.
%See lipics-manual.pdf for further information.
%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
%for section-numbered lemmas etc., use "numberwithinsect"
%for enabling cleveref support, use "cleveref"
%for enabling cleveref support, use "autoref"

@@

%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory

\bibliographystyle{plainurl}% the mandatory bibstyle

\title{A* with Perfect Potentials} %TODO Please add

% \titlerunning{Dummy short title}%optional, please use if title is longer than one line

\author{Ben Strasser}{Germany}{academia@ben-strasser.net}{TODO}{}%TODO mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty. Please provide at least the name of the affiliation and the country. The full address is optional

\author{Tim Zeitz}{Institute of Theoretical Informatics, Algorithmics I, Karlsruhe Institute of Technology, Germany}{tim.zeitz@kit.edu}{}{}

\authorrunning{B. Strasser and T. Zeitz}%TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'

\Copyright{Ben Strasser and Tim Zeitz}%TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/

\ccsdesc[500]{Theory of computation~Shortest paths}
% \ccsdesc[500]{General and reference}%TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm

\keywords{shortest path, road graphs, goal-directed search, contraction hierarchy}%TODO mandatory; please add comma-separated list of keywords

% \category{}%optional, e.g. invited paper

% \relatedversion{}%optional, e.g. full version hosted on arXiv, HAL, or other respository/website
%\relatedversion{A full version of the paper is available at \url{...}.}

% \supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...

%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors. Please enter author specific funding statements as fifth argument of the \author macro.

% \acknowledgements{I want to thank \dots}%optional

%\nolinenumbers %uncomment to disable line numbering

%\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \EventEditors{John Q. Open and Joan R. Access}
% \EventNoEds{2}
% \EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
% \EventShortTitle{CVIT 2016}
% \EventAcronym{CVIT}
% \EventYear{2016}
% \EventDate{December 24--27, 2016}
% \EventLocation{Little Whinging, United Kingdom}
% \EventLogo{}
% \SeriesVolume{42}
% \ArticleNo{23}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\hideLIPIcs
\nolinenumbers

@@

\maketitle

\begin{abstract}
Efficiently computing flexible and optimal routes in continental-sized road networks is a tough challenge.
While Dijkstra's algorithm can be used to solve these problems, it is too slow for many practical applications.
A* is the classical approach to accelerate Dijkstra's algorithm and is used in many fields such as Experimental Algorithms, Robotics, or Artificial Intelligence.
However, A*'s performance depends on the availability of a good potential, also called heuristic, function.
Computing a good potential is a challenge of its own.
To avoid the need for a potential, many hierachical speedup techniques have been developped.
They achieve speed and optimality but sacrifize flexibility.
In this paper, we use hierarchical techniques to compute potential functions.
With this approach, we combine some of the hierarchical speed with the flexibility offered by A* - the best of both worlds - while retaining optimality.
\end{abstract}

@@

\begin{wrapfigure}{r}{3.5cm}

@@

\end{wrapfigure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{fig/scaled_weights.pdf}
\caption{Query running times for queries of DIMACs Europe with scaled edge weights.}\label{fig:scaled_weights}
\end{figure}

@@

\begin{table}
\centering
\caption{Query performance with the different algorithmic features.}\label{tab:building_blocks}
\begin{tabular}{lrrr}
\toprule
{} & Running Time &     Queue Pops &   Relaxed Arcs \\
{} &         [ms] & [$\cdot 10^3$] & [$\cdot 10^6$] \\
\midrule
No Deg2, No Deg3, No SCC, No Pot. & 1765 & 7087.0 & 19.6 \\
No Deg2, No Deg3, No Pot.         & 1308 & 6249.8 & 17.3 \\
No Deg3, No Pot.                  & 1180 & 5233.7 & 16.5 \\
No Pot.                           &  901 & 3035.5 & 15.1 \\
No Deg2, No Deg3, No SCC          &  547 & 1006.4 &  2.7 \\
No Deg2, No Deg3                  &  469 &  905.2 &  2.5 \\
No Deg3                           &  410 &  767.5 &  2.4 \\
                                  &  315 &  445.0 &  2.2 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}
\centering
% TODO dijkstra baseline, preprocessing
\caption{Performance for different applications.}\label{tab:applications}
\begin{tabular}{llrrrrr}
\toprule
        &                     &   Running &     Pot. Eval. &             Relaxed & Avg. length & Affected \\
        &                     & time [ms] & $[\cdot 10^3]$ & arcs $[\cdot 10^3]$ &    increase &     [\%] \\
\midrule
OSM Ger & No Tunnels          &      39.4 &         3874.1 &               290.6 &        1.74 &     83.5 \\
        & No Highways         &     338.5 &        30383.1 &              2555.9 &        6.24 &     95.0 \\
        & Mapbox Live         &      96.5 &         9310.9 &               733.7 &        1.12 &     95.0 \\
\addlinespace
DIMACs  & Fastest $\times 10$ &       1.0 &           69.2 &                 2.7 &        1.00 &     16.5 \\
Europe  & Fastest $\times 2$  &       1.0 &           68.9 &                 2.7 &        1.00 &     16.5 \\
        & Random $\times 10$  &       1.1 &           80.9 &                 3.0 &        1.00 &      1.0 \\
        & Random $\times 2$   &       1.0 &           76.7 &                 2.9 &        1.00 &      1.0 \\
\addlinespace
Ger06   & TD                  &       4.8 &          417.2 &                33.1 &        1.03 &     99.5 \\
Eur17   & TD                  &      98.5 &         5143.8 &               553.3 &        1.04 &     98.5 \\
\bottomrule
\end{tabular}
\end{table}

@@

\bibliography{references}

>>>>

\documentclass[sigconf]{acmart}
%This is a template for producing LIPIcs articles.
%See lipics-manual.pdf for further information.
%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
%for section-numbered lemmas etc., use "numberwithinsect"
%for enabling cleveref support, use "cleveref"
%for enabling cleveref support, use "autoref"

@@

@@

%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{A* with Perfect Potentials}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Ben Strasser}
\email{academia@ben-strasser.net}
\orcid{1234-5678-9012}
\affiliation{}

\author{Tim Zeitz}
\email{tim.zeitz@kit.edu}
\affiliation{%
  \institution{Institute of Theoretical Informatics, Algorithmics I, Karlsruhe Institute of Technology}
  \city{Karlsruhe}
  \country{Germany}
}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
% \renewcommand{\shortauthors}{Strasser and Zeitz}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Efficiently computing flexible and optimal routes in continental-sized road networks is a tough challenge.
While Dijkstra's algorithm can be used to solve these problems, it is too slow for many practical applications.
A* is the classical approach to accelerate Dijkstra's algorithm and is used in many fields such as Experimental Algorithms, Robotics, or Artificial Intelligence.
However, A*'s performance depends on the availability of a good potential, also called heuristic, function.
Computing a good potential is a challenge of its own.
To avoid the need for a potential, many hierachical speedup techniques have been developped.
They achieve speed and optimality but sacrifize flexibility.
In this paper, we use hierarchical techniques to compute potential functions.
With this approach, we combine some of the hierarchical speed with the flexibility offered by A* - the best of both worlds - while retaining optimality.
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

% \ccsdesc[500]{Computer systems organization~Embedded systems}
% \ccsdesc[300]{Computer systems organization~Redundancy}
% \ccsdesc{Computer systems organization~Robotics}
% \ccsdesc[100]{Networks~Network reliability}
\ccsdesc[500]{Theory of computation~Shortest paths}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{shortest path, road graphs, goal-directed search, contraction hierarchy}

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
% \begin{teaserfigure}
%   \includegraphics[width=\textwidth]{sampleteaser}
%   \caption{Seattle Mariners at Spring Training, 2010.}
%   \Description{Enjoying the baseball game from the third-base
%   seats. Ichiro Suzuki preparing to bat.}
%   \label{fig:teaser}
% \end{teaserfigure}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

@@

\begin{figure}

@@

\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{fig/scaled_weights.pdf}
\caption{Query running times for queries of DIMACs Europe with scaled edge weights.}\label{fig:scaled_weights}
\end{figure*}

@@

\begin{table*}
\centering
\caption{Query performance with the different algorithmic features.}\label{tab:building_blocks}
\begin{tabular}{lrrr}
\toprule
{} & Running Time &     Queue Pops &   Relaxed Arcs \\
{} &         [ms] & [$\cdot 10^3$] & [$\cdot 10^6$] \\
\midrule
No Deg2, No Deg3, No SCC, No Pot. & 1765 & 7087.0 & 19.6 \\
No Deg2, No Deg3, No Pot.         & 1308 & 6249.8 & 17.3 \\
No Deg3, No Pot.                  & 1180 & 5233.7 & 16.5 \\
No Pot.                           &  901 & 3035.5 & 15.1 \\
No Deg2, No Deg3, No SCC          &  547 & 1006.4 &  2.7 \\
No Deg2, No Deg3                  &  469 &  905.2 &  2.5 \\
No Deg3                           &  410 &  767.5 &  2.4 \\
                                  &  315 &  445.0 &  2.2 \\
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}
\centering
% TODO dijkstra baseline, preprocessing
\caption{Performance for different applications.}\label{tab:applications}
\begin{tabular}{llrrrrr}
\toprule
        &                     &   Running &     Pot. Eval. &             Relaxed & Avg. length & Affected \\
        &                     & time [ms] & $[\cdot 10^3]$ & arcs $[\cdot 10^3]$ &    increase &     [\%] \\
\midrule
OSM Ger & No Tunnels          &      39.4 &         3874.1 &               290.6 &        1.74 &     83.5 \\
        & No Highways         &     338.5 &        30383.1 &              2555.9 &        6.24 &     95.0 \\
        & Mapbox Live         &      96.5 &         9310.9 &               733.7 &        1.12 &     95.0 \\
\addlinespace
DIMACs  & Fastest $\times 10$ &       1.0 &           69.2 &                 2.7 &        1.00 &     16.5 \\
Europe  & Fastest $\times 2$  &       1.0 &           68.9 &                 2.7 &        1.00 &     16.5 \\
        & Random $\times 10$  &       1.1 &           80.9 &                 3.0 &        1.00 &      1.0 \\
        & Random $\times 2$   &       1.0 &           76.7 &                 2.9 &        1.00 &      1.0 \\
\addlinespace
Ger06   & TD                  &       4.8 &          417.2 &                33.1 &        1.03 &     99.5 \\
Eur17   & TD                  &      98.5 &         5143.8 &               553.3 &        1.04 &     98.5 \\
\bottomrule
\end{tabular}
\end{table*}

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{references}
